---
title: "GO in the head"
author: ""
date: "10/11/2021"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(here)
source(here::here("R/go_functions.R"))
```

## Reading GO enrichment object

```{r cars}
en_head = readRDS(here::here('data/enGo_head.Rds'))
```

## Level 3 blocks

```{r}
goplot_list = llply(en_head$summary$Name[en_head$summary$Nested_Level==3],
                    XGR_plot, en_head$XGR, en_head$summary)
names(goplot_list) = en_head$summary$Name[en_head$summary$Nested_Level==3]
```


### 0-0 - Neuro and sensing

```{r , echo=FALSE}
goplot_list[["0-0"]]
```

### 1-1 - Translation, protein transport, immune response

```{r , echo=FALSE}
goplot_list[["1-1"]]
```


### 2-1 - Sugar metabolism, proteolysis, Krebs Cycle

```{r , echo=FALSE}
goplot_list[["2-1"]]
```


### 3-0 - Development, transcription, splicing, cell respiration

```{r , echo=FALSE}
goplot_list[["3-0"]]
```


### 4-0 - Muscle delevelopment, krebs cycle

```{r , echo=FALSE}
goplot_list[["4-0"]]
```

# Probing some interesting blocks

## Neuro

### 0-0-0

```{r, echo=FALSE}
XGR_plot("0-0-0", en_head$XGR, en_head$summary)
```

Overall: [Gorilla 0-0-0](http://cbl-gorilla.cs.technion.ac.il/GOrilla/t9225cmq/GOResults.html)

- 24 - Regulation, signal transduction, cell component assembly [Gorilla](http://cbl-gorilla.cs.technion.ac.il/GOrilla/guawsy78/GOResults.html)
- 17 - Regulation [Gorilla](http://cbl-gorilla.cs.technion.ac.il/GOrilla/kqzedrl9/GOResults.html)
- 7 - phototransduction, detection of light stimulus, G protein-coupled receptor signaling pathway	[Gorilla](http://cbl-gorilla.cs.technion.ac.il/GOrilla/l41i3m00/GOResults.html)
- 3 - RNA processing [Gorilla](http://cbl-gorilla.cs.technion.ac.il/GOrilla/oyxkgskl/GOResults.html)
- 0 - neuropeptide signaling pathway, synaptic vesicle [transport|localization|exocytosis], synapse  [Gorilla](http://cbl-gorilla.cs.technion.ac.il/GOrilla/m3m7vxbz/GOResults.html)

### 12-0-0

```{r, echo=FALSE}
XGR_plot("12-0-0", en_head$XGR, en_head$summary)
```

Overall: [Gorilla 12-0-0](http://cbl-gorilla.cs.technion.ac.il/GOrilla/pf4211os/GOResults.html)

- 29 - trans-synaptic signaling [Gorilla](http://cbl-gorilla.cs.technion.ac.il/GOrilla/5rjvkbnh/GOResults.html)
- 37 - [cell|neuron] recognition [Gorilla](http://cbl-gorilla.cs.technion.ac.il/GOrilla/b0f7z1bu/GOResults.html)
- 48 - [reproductive|mating] behavior [Gorilla](http://cbl-gorilla.cs.technion.ac.il/GOrilla/dhry9dhc/GOResults.html)
- 53 - Nada! Zilch! Nothing! [Gorilla]()

## Translation

### 1-1-1

```{r, echo=FALSE}
XGR_plot("1-1-1", en_head$XGR, en_head$summary)
```

Overall: [Gorilla 1-1-1](http://cbl-gorilla.cs.technion.ac.il/GOrilla/pf4211os/GOResults.html)

